### 2023-07-20 manuscript.tex
Added TODO about outdated chapter 1 reference

\section{Materials and methods}
\subsection{Alignment and species tree provenance}
Alignments of 8,566 single copy orthologs and the corresponding outputs of the missing data phylo-HMM were obtained from the analyses conducted in chapter~\ref{chapter:1}. Likewise, the LG consensus tree generated by the ``non-invariant, 100\% redundancy'' sampling strategy was used as the input or reference where indicated in subsequent phylogenetic analyses.

>>>>

\section{Materials and methods}
\subsection{Alignment and species tree provenance}
% TODO: Update text once chapter 1 is published
Alignments of 8,566 single copy orthologs and the corresponding outputs of the missing data phylo-HMM were obtained from the analyses conducted in chapter~1. Likewise, the LG consensus tree generated by the ``non-invariant, 100\% redundancy'' sampling strategy was used as the input or reference where indicated in subsequent phylogenetic analyses.
